---
title: "Conformity of Norms Replication Analysis"
author: "Group 5"
date: "August 27,2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = F, message = F, warning = F)
```

### Analysis based on the original analysis scripts of 

> Pryor C, Perfors A, Howe PDL (2019)
Conformity to the descriptive norms of people with
opposing political or social beliefs. PLoS ONE 14
(7): e0219464. https://doi.org/10.1371/journal.
pone.0219464

### Their original repository can be found [here](https://osf.io/tgf96/?view_only=7dc67fcc0c1f4fdea8fe1dfe5d492480)

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}

library(ordinal)
library(tidyverse)
library(rstan)
library(bridgesampling)
library(shinystan)
library(dplyr)
library(brms)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
set.seed(123)

# global color scheme / non-optimized
project_colors = c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")

# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = project_colors)
}
scale_fill_discrete <- function(...) {
   scale_fill_manual(..., values = project_colors)
} 

# nicer global knitr options
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
                      cache = TRUE, fig.align = 'center')

```


### Importing the data

```{r, results='hide'}

df_cleaned <- read_csv("02_clean_data.csv")

```

### Glimps at the data

```{r}

df_cleaned %>% 
  head()

```
```{r}

df_cleaned %>% 
  glimpse()

```

### Frequentist Analysis: ` Effect sizes `

```{r}

# cumulative link models
ordinal <- clm(as.factor(response)~ingroupNorm*bothShown, data=df_cleaned)

# coefficients
coefs <- exp(coef(ordinal))

# confidence intervals
CI <- exp(confint(ordinal))

```

```{r}

coefs

```
```{r}

CI

```

### Bayesian analysis
#### Setting up data for stan

```{r}

useable_data <- 
  df_cleaned %>%
  select(
    response, 
    ingroupNorm, 
    bothShown, 
    ingroupAgree, 
    outgroupDisagree
    ) %>% #select relevant columns
  mutate(
    ingroupAgree = 
      ifelse(is.na(ingroupAgree), 1, ingroupAgree), 
    outgroupDisagree = 
      ifelse(is.na(outgroupDisagree), 1, outgroupDisagree)
    ) # We assumed that participants identified with the ingroup and not with the outgroup.

stan_data <- as.list(
  c(
    useable_data, 
    N = dim(useable_data)[1]
    )
  )

```


### Fitting ` Self-categorization theory ` model

```{r}

fit_SCT <- 
  stan(
    file = "stan_models/SCT.stan", 
    data=stan_data, 
    iter=10000, 
    chains=4, 
    seed=123, 
    control=
      list(
        adapt_delta = 0.99
        )
    )

```

### Fitting the ` alternative ` model

```{r}

fit_herding <- 
  stan(
    file = "stan_models/herding.stan", 
    data=stan_data, 
    iter=10000, 
    chains=4, 
    control=
      list(
        adapt_delta = 0.99
        )
    )

```

### ` Model comparison ` using Bayes Factors

```{r}

marg_lik_SCT <- 
  bridge_sampler(
    samples = fit_SCT
    )

marg_lik_herding <- 
  bridge_sampler(
    samples = fit_herding
    )

bridgesampling::bf(
  marg_lik_herding,
  marg_lik_SCT
  )

```

